Designing and modeling a browser-based distributed evolutionary computation systems

### 2015-04-02 modeling-volunteer-computing-gecco.tex
Some corrections

The server program includes also additional logic for logging to
different files or services, routes to obtain information from the
server, such as the anonymized IPs that have participated in the experiment, and code to serve the static pages
and the JavaScript/CSS
code also. Additionally to the code in the previous paper
\cite{arxiv:modeling} this version restarts the chromosome pool when
the experiment has finished; it includes a configurable termination
condition that checks for the solution and empties the chromosome pool
and logs the end of the experiment. This allows us to run continuously
experiments without restarting the server by hand as we did in the
previous version.

All in all, it amounts to a few hundred lines of code
including all languages. This code can
be deployed, in principle, in any server that is able to run node.js, but for the
purposes of this experiment OpenShift (\url{http://openshift.com}), a Platform as a Service with a
free tier, has been chosen. It could be also be deployed, with small
or no modification, to Heroku or other similar PaaS. Any of them are
free up to a certain level of use and thus fulfill the requirement of
using free resources as a sustainable way of performing distributed
evolutionary compuation experiments \cite{Merelo2014,jj:idc:lowcost}.

>>>>

The server program includes also additional logic for logging to
different files or services, routes to obtain information from the
server, such as the anonymized IPs that have participated in the
experiment, the ordinal number of the experiment that is being performed or the content of the chromosome pool, and code to serve the static pages
and the JavaScript/CSS
code also. The main changes to the code from the  the previous paper
\cite{arxiv:modeling} is, besides the inclusion of logging for a
better experiment analyis, the function that checks for the algorithm
termination condition and restarts the chromosome pool when
it does; it includes a configurable termination
condition that checks for the solution and empties the chromosome pool
and logs the end of the experiment. This allows us to run continuously
experiments without restarting the server by hand as we did in the
previous version.

All in all, it amounts to a few hundred lines of code
including all languages (client and server JavaScript, HTML and CSS). This code can
be deployed, in principle, in any server that is able to run node.js, but for the
purposes of this experiment OpenShift (\url{http://openshift.com}), a Platform as a Service with a
free tier, has been chosen. It could be also be deployed, with small
or no modification, to Heroku or other similar PaaS. Any of them are
free up to a certain level of use and thus fulfill the requirement of
using free resources as a sustainable way of performing distributed
evolutionary compuation experiments \cite{Merelo2014,jj:idc:lowcost}.
